% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Work Experience
\sectionTitle{Professional Experience}{\faSuitcase}
\begin{experiences}
  \experience
    {November 2022- } {Empirico Inc}{Bioinformatics Engineer}{Remote}
    {Present} {
    \begin{itemize}
    \item Built pipelines and containerized key infrastructure for variant annotation.
    \item Refactored legacy cross-platform genomics data integration pipelines on Databricks and DNAnexus.
    \item Orchestrated large scale GWAS analyses under tight deadlines.
    \item Performed data analysis and visualizations for quality control in genomics data.
    \end{itemize}
    \cvtag{Python}\cvtag{Pyspark}\cvtag{Databricks}\cvtag{Hail}\cvtag{DeltaLake}\cvtag{AWS}\cvtag{Dagster}\cvtag{DNAnexus}\cvtag{Scala}
    }

  \emptySeparator

  \experience
    {July 2020 -} {The Scripps Research Institute}{Research Programmer III}{San Diego, CA}
    {November 2022} {
    \begin{itemize}
    \item Lead developer of mygeneset.info, a database and REST API for managing collections of genes.
    \item Developed data plugins to parse and integrate data across various databases.
    \item Wrote unit and integration tests to ensure data integrity across various databases.
    \item Set up a production web server and oversaw deployment of several projects to AWS.
    \end{itemize}
    \cvtag{Python}\cvtag{Elasticsearch}\cvtag{MongoDB}\cvtag{AWS}\cvtag{Nginx}\cvtag{Tornado}\cvtag{Docker}
    }

  \emptySeparator

  \experience
    {August 2019 -} {Co-op | GlaxoSmithKline (GSK)}{Data Analysis \& Visualization}{Upper Providence, PA}
    {February 2020} {
    \begin{itemize}
    \item Used Databricks and the Microsoft Azure cloud platform for running distributed text analytics (sentiment analysis).
    \item Constructed a DevOps pipeline for continuous integration and deployment on a data dashboard.
    \item Created data visualization dashboards using Microsoft's Power BI, and TIBCO Spotfire.
    \item Used JavaScript to design and implement a protein structure viewer in a Spotfire dashboard.
    \item Provided data visualization consultancy to various other teams across R\&D.
    \end{itemize}
    \cvtag{Mirosoft Azure}\cvtag{Databricks}\cvtag{PowerShell}\cvtag{Spotfire}\cvtag{PowerBI}
    }

  \emptySeparator

  \experience
    {May 2019 -} {Internship | GlaxoSmithKline (GSK)}{Protein Design \& Informatics}{Upper Providence, PA}
    {August 2019}    {
        \begin{itemize}
        \item Maintained a Python module for accessing protein structure data from an in-house API, and deployed it as a Conda package.
        \item Built a large dataset of ligand-to-domain associations from protein structure and sequence data.
        \item Wrote a Python pipeline for running BLAST and HHMER searches on a large dataset of protein sequences.
        \item Contributed code and data towards the development of a new target tractability pipeline.
        \end{itemize}
    \cvtag{Python}\cvtag{HPC}\cvtag{Data Integration}\cvtag{BLAST}\cvtag{HHMER}\cvtag{Protein structures}
    }

  \emptySeparator

  \experience
    {May 2018 -} {Internship | GlaxoSmithKline (GSK)}{Protein Design \& Informatics}{Upper Providence, PA}
    {August 2018} {
        \begin{itemize}
        \item Ran scalability benchmarks to optimize molecular dynamics (MD) simulation performance in GPU clusters.
        \item Evaluated MD simulation methods for identifying cryptic binding pockets in proteins.
        \item Wrote Python scripts to automate large scale MD data analysis.
        \item Ran a high-throughput homology modeling pipeline using Rosetta via Docker containers in an HPC environment.
        \item Used Molecular Operating Environment (MOE) for pocket detection in proteins and analyzed its accuracy.
        \end{itemize}
        \cvtag{Python}\cvtag{Tcl}\cvtag{Molecular Dynamics}\cvtag{MOE}\cvtag{Docker}\cvtag{HPC}\cvtag{PyMOL}
        \cvtag{VMD}\cvtag{Homology Modeling}
    }


  % \experience
  %   {January 2019 -} {Teaching Assistant | Computational Modeling of Biostructures}{UTEP Bioinformatics Program}{El Paso, TX}
  %   {May 2019}    {
  %       \begin{itemize}
  %       \item Organized and prepared hands-on labs and homework assignments.
  %       \item Taught students basic UNIX shell commands, and writing scripts for automating tasks.
  %       \item Trained students in using molecular modeling tools, such as UCSF Chimera and Coot.
  %       \item Taught students the basics of crystallography data processing.
  %       \item Taught students the basics of solving  cryo-EM structures using Relion.
  %       \end{itemize}
  %       \cvtag{Bash}\cvtag{Chimera}\cvtag{Coot}\cvtag{Relion}\cvtag{EMAN2}
  %   }

  % \emptySeparator

  % \experience
  %   {January 2018 -} {Research Assistant | Structure-Based Drug Discovery Lab}{UTEP School of Pharmacy}{El Paso, TX}
  %   {May 2019} {
  %       \begin{itemize}
  %       \item Developed and tested machine-learning scoring functions for the prediction of drug-target binding affinities, logP, and other pharmacokinetic properties.
  %       \item Wrote code for performing cluster cross-validation based on molecular fingerprints.
  %       \item Generated datasets of pharmacokinetic data by mining web resources and literature.
  %       \item Generated large decoy sets for assessing ligand docking.
  %       \end{itemize}
  %       \cvtag{Bash}\cvtag{Python}\cvtag{Scikit-learn}\cvtag{HPC}
  %   }

  % \emptySeparator

  % \experience
  %   {August 2016 -} {Research Assistant | Bioinformatics}{UTEP Bioinformatics Program}{El Paso, TX}
  %   {August 2017} {
  %       \begin{itemize}
  %       \item Learned to use molecular docking software (AutoDock and Schrödinger Glide)
  %       \item Performed pocket detection and pharmacophore analysis using Schrödinger tools.
  %       \item Benchmarked molecular docking tools against several GPCR receptors with crystal structures.
  %       \end{itemize}
  %       \cvtag{Python}\cvtag{Bash}\cvtag{Molecular docking}\cvtag{HPC}
  %   }

  % \emptySeparator

  % \experience
  %   {March 2014 -} {Undergraduate Research Assistant | Structural Biochemistry Lab}{UTEP Dept. of Chemistry}{El Paso, TX}
  %   {August 2015} {
  %       \begin{itemize}
  %       \item Transformation of recombinant plasmids in BL21 cells.
  %       \item Bacterial expression and purification of proteins.
  %       \item Functional assays to evaluate protein folding activity.
  %       \item Learned to use Cryo-EM image processing software for 3D protein structure determination.
  %       \end{itemize}
  %       \cvtag{Protein Expression}\cvtag{Protein Purification}\cvtag{Cryo-EM processing}\cvtag{Relion}\cvtag{EMAN2}\cvtag{Bash}
  %   }


\end{experiences}
