% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)


\sectionTitle{Presentations}{\faLaptop}
\begin{scholarship}
    \scholarshipentry{2018}
					{(Poster) \textit{Evaluating the effectiveness of mixed probe molecular dynamics for cryptic pocket detection}.  \textbf{GSK Intern/Co-op symposium}, Upper Providence, Pennsylvania, USA.}
	\scholarshipentry{2018}
					{(Poster) \textit{Automated workflow for reproducible analysis of protein-ligand scoring functions}.  \textbf{OpenEye CUP XVIII},  Santa Fe, New Mexico, USA.}
	\scholarshipentry{2016}
					{(Poster) \textit{Comparison of AutoDock and Glide in docking Suvorexant to the crystal structure of human OX2 receptor (hOX2R)} \textbf{19th UTEP/NMSU Workshop on Mathematics, Computer Science, and Computational Sciences}, El Paso, Texas, USA.}
	\scholarshipentry{2015}
					{(Poster) \textit{A point mutation in the Phi-EL chaperonin alters ring separation and protein folding activity}.  \textbf{ UTEP COURI Symposium}, El Paso, Texas, USA.}
\end{scholarship}

\sectionTitle{Workshops}{\faGroup}
\begin{experiences}
 \experience
    {May 7-9, 2018} {MMTF Workshop \& Hackathon}{San Diego Supercomputer Center (SDSC)}{ San Diego, CA}
    {}    {
        \begin{itemize}
        \item Learned about the Protein Data Bank's Macromolecular Transmission Format (MMTF) and its applications for structural data mining.
        \item Learned to render protein structures inside Jupyter notebooks with NGLView.
        \item Was introduced to using Apache Spark with Python (Pyspark), and Spark SQL for big data analysis.
        \item Hackathon project: Wrote a script to characterize close residue contacts in the PDB database.
        \end{itemize}
    }

\emptySeparator

\experience
    {August 28, 2019} {Dashboard in a Day}{Microsoft}{Malvern, PA}
    {}    {
        \begin{itemize}
        \item Learned to use Microsoft's Power BI to ingest and transform data, and develop interactive dashboards.
        \end{itemize}
    }
\end{experiences}